---
title: "Stem Rot"
author: "Zhang Zhenglin"
output:
  pdf_document:
    toc: yes
  html_notebook:
    toc: yes
    toc_float: yes
editor_options:
  markdown:
    wrap: sentence
---

# Necessary libraries

```{r echo=FALSE,message=FALSE,warning=FALSE}
library(knitr)
library(ggplot2)
theme_set(theme_bw())
library(emmeans)
library(multcomp)
library(PLS205)
library(lme4)
library(lmerTest)
library(multcompView)
library(car)
library(Rmisc) 
library(dplyr) #https://r4ds.had.co.nz/ (Chapter 3, Chapter 5, look at filter and select)
# https://bookdown.org/ansellbr/WEHI_tidyR_course_book/
library(stringr) 
library(data.table)
library(GGally)
library(formatR)
library(readxl)
library(mgcv)
library(xlsx)

```

# Data Organisation

## Read from excel and getting weighted average score

> Each plot had 25 tillers graded for disease serverity. Each tiller had a grading from 0-4, where 0 is healthy and 4 is a trainwreck. Total score is the sum of the products of number of tillers at each severity rating. i.e. number of tilles at a rating of 1 x 1 + number of tilles at a rating of 1 x 2.... Weighted average is total score divided by the number of tillers scored i.e. Total_Score/25. 

```{r}
master <- read_excel("StemRot_Master.xlsx", sheet = 1)
master <- mutate_if(master, is.character, as.factor)
master$Year <- as.factor(master$Year)
master$Blk <- as.factor(master$Blk)

master$Total_Score <- (master$One*1)+(master$Two*2)+(master$Three*3)+(master$Four*4)+(master$Five*5)
master$Weighted_Average <- master$Total_Score/25
master$total_plants <- (master$One)+(master$Two)+(master$Three)+(master$Four)+(master$Five)

table(master$total_plants)

#checked that all is okayyyyyy and have 25 tillers

str(master)
```


# Initial visualisation

Just purely based on visual inspection, CR has higher disease severity than FR. 

```{r}
ggplot(master, aes(y=Weighted_Average, x=Year, color=Treatment))+ 
  geom_point()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size= 9))
```

# ANOVA (Main text results taken from here: Figure 5)

```{r}
disease_model <- lmer(Weighted_Average~Treatment*Year+(1|Blk), data = master)

pls205_diagnostics(disease_model, EU = "Blk")

anova(disease_model)

Treatment_means = emmeans(disease_model,spec = 'Treatment',by = 'Year')
Treatment_effects = contrast(Treatment_means, method = 'pairwise', adjust = "Tukey")

summary(Treatment_effects) 
cld(Treatment_means)

Treatment_effects_summary <- 
  as.data.frame(summary(Treatment_effects)) %>%
   mutate(
    p_value = case_when(
      p.value < 0.05 ~ "*",           # For p-values less than 0.01
      TRUE ~ sprintf("%.2f", p.value)     # Force two decimal places for all other p-values
    )
  )
```



# Graphing dataframe

```{r}
graphing <- master %>% 
    group_by(Treatment, Year) %>% 
   mutate(Weighted_Average_se = sd(Weighted_Average)/sqrt(3)) %>% 
  summarise(Weighted_Average = mean(Weighted_Average),
            Weighted_Average_se = mean(Weighted_Average_se)) %>%
  left_join(Treatment_effects_summary %>% select(Year, p_value), by = "Year")
```
# Graph


```{r}
Disease_graph_bar <-
  ggplot(graphing, aes(x = Year, y = Weighted_Average, fill = Treatment)) +
  #geom_boxplot()+
  geom_bar(stat = "identity", position = "dodge", width = 0.7) +
  labs(x = "Year", y = "Weighted_Average", fill = "Treatment") +
  scale_fill_manual(values = c("#0072B2","#FFCC66"),labels = c("Continuous Rice (CR)", "Fallow Rice (FR)"))+
  geom_errorbar(aes(ymin=Weighted_Average-Weighted_Average_se, ymax=Weighted_Average+Weighted_Average_se), width=.2,position=position_dodge(0.7))+
  scale_y_continuous(name="Stem rot disease index", limits = c(0, 5),  expand = c(0, 0))+
  coord_cartesian(ylim = c(1, 5))+
  scale_x_discrete(name="")+
  theme_classic()+
  theme(axis.text.x = element_text(size= 12),
        axis.text.y = element_text(size= 12),
        axis.title = element_text(size=15),
        legend.title = element_text(size = 15),
        legend.text = element_text(size = 12))+
  geom_text(data = graphing %>% filter(Treatment == "CR"),
            aes(x = Year, y = Weighted_Average+ 0.5, label = p_value), size =10)+
  #geom_vline(xintercept = 3.5, linetype = "dashed", color = "black", size = 1.1)+
  theme(legend.position = "bottom")
            

Disease_graph_bar

ggsave(Disease_graph_bar, 
       filename = "Disease_graph_bar.png", 
       path = "D:/Academics/UC Davis/School Work/Linquist Lab/Data/R stats/Agronomic paper/Figures",
       height = 15, 
       width = 15, 
       units = "cm", 
       dpi = 300)
```

# Pairwise pooled 

```{r}
Treatment_means_average = emmeans(disease_model,spec = 'Treatment')
Treatment_effects_average = contrast(Treatment_means_average, method = 'pairwise', adjust = "Tukey")

summary(Treatment_effects_average) 
cld(Treatment_means_average)

Treatment_effects_summary_average <- 
  as.data.frame(summary(Treatment_effects_average)) %>%
   mutate(
    p_value = case_when(
      p.value < 0.05 ~ "*",           # For p-values less than 0.01
      TRUE ~ sprintf("%.2f", p.value)     # Force two decimal places for all other p-values
    )
  )
```