---
title: "N Rate Trial (no topdress)"
author: "Zhang Zhenglin"
output:
  pdf_document:
    toc: yes
editor_options:
  markdown:
    wrap: true
---

# Necessary libraries

```{r echo=FALSE,message=FALSE,warning=FALSE}
library(knitr)
library(ggplot2)
theme_set(theme_bw())
library(emmeans)
library(multcomp)
library(PLS205)
library(lme4)
library(lmerTest)
library(multcompView)
library(car)
library(Rmisc) 
library(dplyr) #https://r4ds.had.co.nz/ (Chapter 3, Chapter 5, look at filter and select)
# https://bookdown.org/ansellbr/WEHI_tidyR_course_book/
library(stringr) 
library(data.table)
library(GGally)
library(formatR)
library(readxl)
library(mgcv)
library(xlsx)
library(writexl)
library(ggpubr)
```

# Data Organisation

## Read from excel

```{r}
master <- read_excel("master_yields.xlsx", sheet = 1)
master$Treatment <- master$Field
master <- mutate_if(master, is.character, as.factor)
master$NrateF <- as.factor(master$Nrate)
master$Year <- as.factor(master$Year)
master$Yield_Mgha <- master$Yield_kgha/1000

str(master)
```


# Initial visualisation

```{r}
ggplot(master, aes(y=Yield_Mgha, x=Nrate, color=Field))+ 
  geom_point()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size= 9))
```

# Check for most important variables

> Year effect very significant. So analyse data by 3 different years. 

```{r}
all_factors_model <- lm(Yield_Mgha~Year+Blk+NrateF+Field+Topdressed, data = master)

pls205_diagnostics(all_factors_model)

anova(all_factors_model)
```

# Subset data from the 3 years

```{r}
#master$main_plot <- paste(master$Blk, master$Treatment, sep="_")
#master$modular <- paste(as.numeric(master$Blk)%%3, master$Treatment, sep = "_")
notopdress <- master %>% filter (Topdressed != 1)

yield_average <- notopdress
yield_2021 <- notopdress %>% filter (Year == "2021")
yield_2022 <- notopdress %>% filter (Year == "2022")
yield_2023 <- notopdress %>% filter (Year == "2023")
#checked datasets, all looks good. 
```

# Treatment and year effect (Corresponds to Table 1: ANOVA)

```{r}
model_all_years <- lmer(Yield_Mgha ~ Treatment*Year++NrateF+NrateF:Treatment+Treatment:Year+(1|Blk:Treatment)+(1|Blk), data = yield_average)
#lm(Yield_Mgha ~ Treatment*Year, data = yield_average)

pls205_diagnostics(model_all_years, EU ="Blk:Treatment")
pls205_diagnostics(model_all_years, EU ="Blk")

anova(model_all_years)

field_means_all_years = emmeans(model_all_years,spec = 'Treatment',by = 'Year')
field_effects_all_years = contrast(field_means_all_years, method = 'pairwise', adjust = "Tukey")
summary(field_effects_all_years) 
cld(field_means_all_years)

anova_results <- as.data.frame(anova(model_all_years))
```

# Quadratic models

## Automating the process with functions

We will be assuming that the yield-nrate curve will follow a quadratic curve. It will be messy to extract all the coefficients and then compute local maxima of each treatment. So here is a function to do that. 

```{r}
#this function automates the extraction of coefficients from quadratic models to calculate optimal N rates and maximum yields

optimal_N <- function(model) {
  # Extract the coefficients
  coefficients <- coef(model)
  
  # Get the names of the terms to make sure we handle your model's naming conventions
  term_names <- names(coefficients)
  
  # Identify the names for the intercept, linear, and quadratic terms
  intercept_term <- "(Intercept)"
  linear_term <- term_names[grepl("^Nrate", term_names)]
  quadratic_term <- term_names[grepl("I\\(Nrate\\^2\\)", term_names)]
  
  # Ensure both linear and quadratic terms are found
  if (length(linear_term) == 0 | length(quadratic_term) == 0) {
    stop("The model must include both Nrate and I(Nrate^2) terms.")
  }
  
  # Extract individual coefficients
  beta_0 <- coefficients[intercept_term]
  beta_1 <- coefficients[linear_term]
  beta_2 <- coefficients[quadratic_term]
  
  # Calculate the optimal N rate (x value) where the slope is zero
  x_optimal <- -beta_1 / (2 * beta_2)
  
  # Calculate the corresponding y value at the optimal N rate
  y_optimal <- beta_0 + beta_1 * x_optimal + beta_2 * x_optimal^2
  
  # Return both x and y values as a list
  return(list(x_optimal = x_optimal, y_optimal = y_optimal))
}

#this function automates the construction of quadratic models

run_all_models <- function() {
  # Create an empty data frame to store the results
  results <- data.frame(
    Year = character(),
    Treatment = character(),
    Nrate_optimal = numeric(),
    Yield_max = numeric(),
    stringsAsFactors = FALSE
  )
  
  # Define the years and treatments
  years <- c(2021, 2022, 2023, "average")
  treatments <- c("CR", "FR")
  
  # Loop through each year and treatment
  for (year in years) {
    for (treatment in treatments) {
      # Construct the model name dynamically
      model_formula <- as.formula(paste0("Yield_Mgha ~ Nrate + I(Nrate^2)"))
      data_name <- paste0("yield_", year)
      model_data <- get(data_name) %>% filter(Treatment == treatment)
      
      # Fit the model for the current year and treatment
      model <- lm(model_formula, data = model_data)
      
      # Calculate optimal Nrate and maximum yield using the optimal_N function
      optimal_values <- optimal_N(model)
      
      # Add the results to the data frame
      results <- rbind(results, data.frame(
        Year = year,
        Treatment = treatment,
        Nrate_optimal = optimal_values$x_optimal,
        Yield_max = optimal_values$y_optimal
      ))
    }
  }
  
  return(results)
}

```

## Quadratic regressions and optimal N rates

```{r}
#Here are all the optimal N rates

optimal_results <- run_all_models()

optimal_results

optimal_results$Year <- as.factor(optimal_results$Year)

quadraticModel_2023_FR <- lm(Yield_Mgha ~ I(Nrate) + I(Nrate^2), data= yield_2023 %>% filter(Treatment=="FR"))

summary(quadraticModel_2023_FR)

write_xlsx(optimal_results, "C:/Users/zhang/Documents/GitHub/FallowRice_ContinuousRice_AgronomicPerformance/Yield/optimalNrates.xlsx")
```


# Data visualisation and statistical testing (Corresponds to Figure 2)

## Graphing dataframes

```{r}
# 2021 dataframe

yield_2021_dataframe <- yield_2021 %>% 
    group_by(Treatment, Nrate) %>% 
   mutate(Yield_Mgha_se = sd(Yield_Mgha)/sqrt(3)) %>% 
  summarise(Yield_Mgha = mean(Yield_Mgha),
            Yield_Mgha_se = mean(Yield_Mgha_se)) %>%
  mutate(Year = "2021")%>%
  left_join(optimal_results %>% select(Year, Treatment, Nrate_optimal), by = c("Year", "Treatment"))%>%
  mutate(Nrate_optimal = round(Nrate_optimal))


# 2022 dataframe

yield_2022_dataframe <- yield_2022 %>% 
    group_by(Treatment, Nrate) %>% 
   mutate(Yield_Mgha_se = sd(Yield_Mgha)/sqrt(3)) %>% 
  summarise(Yield_Mgha = mean(Yield_Mgha),
            Yield_Mgha_se = mean(Yield_Mgha_se)) %>%
  mutate(Year = "2022")%>%
  left_join(optimal_results %>% select(Year, Treatment, Nrate_optimal), by = c("Year", "Treatment"))%>%
  mutate(Nrate_optimal = round(Nrate_optimal))

# 2023 dataframe

yield_2023_dataframe <- yield_2023 %>% 
    group_by(Treatment, Nrate) %>% 
   mutate(Yield_Mgha_se = sd(Yield_Mgha)/sqrt(3)) %>% 
  summarise(Yield_Mgha = mean(Yield_Mgha),
            Yield_Mgha_se = mean(Yield_Mgha_se)) %>%
  mutate(Year = "2023")%>%
  left_join(optimal_results %>% select(Year, Treatment, Nrate_optimal), by = c("Year", "Treatment"))%>%
  mutate(Nrate_optimal = round(Nrate_optimal))

# average dataframe

yield_average_dataframe <- yield_average %>% 
    group_by(Treatment, Nrate) %>% 
   mutate(Yield_Mgha_se = sd(Yield_Mgha)/sqrt(3)) %>% 
  summarise(Yield_Mgha = mean(Yield_Mgha),
            Yield_Mgha_se = mean(Yield_Mgha_se)) %>%
  mutate(Year = "average")%>%
  left_join(optimal_results %>% select(Year, Treatment, Nrate_optimal), by = c("Year", "Treatment"))%>%
  mutate(Nrate_optimal = round(Nrate_optimal)) 
```

## 2021 

### Statical test, comparisons by N rate and Treatment

```{r}
model_2021 <- lmer(Yield_Mgha ~ NrateF*Treatment+(1|Blk:Treatment)+(1|Blk), data=yield_2021)

anova(model_2021)

field_means_2021 = emmeans(model_2021,spec = 'Treatment',by = 'NrateF')
field_effects_2021 = contrast(field_means_2021, method = 'pairwise', adjust = "Tukey")

summary(field_effects_2021) 
cld(field_means_2021)

emmeans(model_2021, ~ Treatment + NrateF)
cld_2021 <- cld(emmeans(model_2021, ~ Treatment + NrateF),adjust = "Sidak")

cld_2021

top_yields_2021 <- cld_2021 %>%
  group_by(Treatment) %>%
  filter(emmean == max(emmean)) %>%
  ungroup()
```


### Graph_2021

```{r}
N_response_curve_2021 <- 
ggplot(yield_2021_dataframe, aes(x=Nrate, y=Yield_Mgha, color=Treatment))+
  geom_point(data=yield_2021_dataframe, size=2.5)+ #this is the mean values
  geom_point(data=yield_2021, size=1, alpha=0.4)+ #this are the raw values
  scale_color_manual(values=c("#0072B2","#FFCC66"), name = "Treatment", labels = c('Continuous Rice (CR)','Fallow Rice (FR)'))+
  scale_x_continuous(name=expression("N rate (kg N ha"^{-1}*")"), limits = c(-20, 320), breaks = seq(0, 300, by=50), expand =c(0,0))+
  #scale_x_continuous(name=expression("N rate (kg N ha"^{-1}*")"), limits = c(-20, 280), breaks = c(0, 115, 155, 185, 225, 260), expand =c(0,0))+ #limits = c(0, 
  scale_y_continuous(name= expression("Yield (Mg ha"^{-1}*")"), limits = c(0, 22), breaks = seq(0, 22, by = 2.5), expand =c(0,0))+ #, limits = c(0, 16000), expand = c(0, 0), breaks =
  #geom_errorbar(data=yield_2021_dataframe, aes(ymin=Yield_Mgha-Yield_Mgha_se, ymax=Yield_Mgha+Yield_Mgha_se), width=8, size=0.7)+
  theme_classic()+
  geom_smooth(data = yield_2021, method = "lm", formula = y ~ poly(x, 2), se = FALSE)+
  #geom_vline(xintercept = c(0, 115, 155, 185, 225, 260), linetype = "twodash", color = "black") +
  stat_regline_equation(data=yield_2021,
                      aes(x=Nrate, y=Yield_Mgha, color=Treatment, group = Treatment, 
                          label = paste(..rr.label..)),
                      formula = y ~ poly(x, 2, raw = TRUE),
                      show.legend = FALSE, label.x = 0, label.y = c(16.5, 19))+
   stat_regline_equation(data=yield_2021,
                      aes(x=Nrate, y=Yield_Mgha, color=Treatment, group = Treatment, 
                          label = paste(..eq.label..)),
                      formula = y ~ poly(x, 2, raw = TRUE),
                      show.legend = FALSE, label.x = 0, label.y = c(17.5, 20))+
  theme(axis.text = element_text(size = 14), axis.title = element_text(size=16))+
  theme(legend.text = element_text(size = 12),legend.title = element_text(size = 14))+
  theme(plot.title = element_text(hjust = 0.5, size = 20, face = "bold"))+
  ggtitle(expression("Yield: 2021"))+
  annotate(
  "text",
  x = c(0),
  y = yield_2021_dataframe %>% 
       filter(Treatment == "FR", Nrate == 0) %>% 
        mutate(Yield_Mgha_plus_higher = Yield_Mgha + 1) %>% 
        pull(Yield_Mgha_plus_higher),
  label = "*",
  size = 7,
  vjust = 0
  )+
# Vertical line for CR
geom_segment(
  aes(x = optimal_results %>% filter(Treatment == "CR", Year == "2021") %>% pull(Nrate_optimal), 
      xend = optimal_results %>% filter(Treatment == "CR", Year == "2021") %>% pull(Nrate_optimal), 
      y = 0,  # Start exactly from 0 on y-axis
      yend = optimal_results %>% filter(Treatment == "CR", Year == "2021") %>% pull(Yield_max)),
  linetype = "twodash", color = "#0072B2", size = 0.6
) +
# Vertical line for FR
geom_segment(
  aes(x = optimal_results %>% filter(Treatment == "FR", Year == "2021") %>% pull(Nrate_optimal), 
      xend = optimal_results %>% filter(Treatment == "FR", Year == "2021") %>% pull(Nrate_optimal), 
      y = 0,  # Start exactly from 0 on y-axis
      yend = optimal_results %>% filter(Treatment == "FR", Year == "2021") %>% pull(Yield_max)),
  linetype = "twodash", color = "#FFCC66", size = 0.6
) +

# Horizontal line for CR
geom_segment(
  aes(y = optimal_results %>% filter(Treatment == "CR", Year == "2021") %>% pull(Yield_max), 
      yend = optimal_results %>% filter(Treatment == "CR", Year == "2021") %>% pull(Yield_max), 
      x = -20,  # Start exactly from 0 on x-axis
      xend = optimal_results %>% filter(Treatment == "CR", Year == "2021") %>% pull(Nrate_optimal)),
  linetype = "twodash", color = "#0072B2", size = 0.6
) +
# Horizontal line for FR
geom_segment(
  aes(y = optimal_results %>% filter(Treatment == "FR", Year == "2021") %>% pull(Yield_max), 
      yend = optimal_results %>% filter(Treatment == "FR", Year == "2021") %>% pull(Yield_max), 
      x = -20,  # Start exactly from 0 on x-axis
      xend = optimal_results %>% filter(Treatment == "FR", Year == "2021") %>% pull(Nrate_optimal)),
  linetype = "twodash", color = "#FFCC66", size = 0.6
)+
      geom_curve(x = top_yields_2021 %>% 
                 filter(Treatment == "FR") %>% 
                 mutate(NrateF = as.numeric(paste(NrateF))) %>% 
                 pull(NrateF)-2, 
                 y = top_yields_2021 %>% 
                 filter(Treatment == "FR") %>% 
                 pull(emmean),
               xend = top_yields_2021 %>% 
                 filter(Treatment == "CR") %>% 
                 mutate(NrateF = as.numeric(paste(NrateF))) %>% 
                 pull(NrateF)-2, 
               yend = top_yields_2021 %>% 
                 filter(Treatment == "CR") %>% 
                 pull(emmean),
               color = 1, size=1,
               curvature = 1.2,)+
  annotate(
  "text",
  x =   (top_yields_2021 %>% 
                 filter(Treatment == "FR") %>% 
                 mutate(NrateF = as.numeric(paste(NrateF))) %>% 
                 pull(NrateF)+
       top_yields_2021 %>% 
                 filter(Treatment == "CR") %>% 
                 mutate(NrateF = as.numeric(paste(NrateF))) %>% 
                 pull(NrateF))/2,
  y = (top_yields_2021 %>% 
                 filter(Treatment == "FR") %>% 
                 pull(emmean)+
           top_yields_2021 %>% 
                 filter(Treatment == "CR") %>% 
                 pull(emmean))/2,
  label = "ns",
  size = 5,
  vjust = 0.3,
  hjust = +2.2 )
  

N_response_curve_2021

```


## 2022 

### Statical test, comparisons by N rate and Treatment

```{r}
model_2022 <- lmer(Yield_Mgha ~ NrateF*Treatment+(1|Blk:Treatment)+(1|Blk), data=yield_2022)

anova(model_2022)

field_means_2022 = emmeans(model_2022,spec = 'Treatment',by = 'NrateF')
field_effects_2022 = contrast(field_means_2022, method = 'pairwise', adjust = "Tukey")

summary(field_effects_2022) 
cld(field_means_2022)

emmeans(model_2022, ~ Treatment + NrateF)
cld_2022 <- cld(emmeans(model_2022, ~ Treatment + NrateF),adjust = "Sidak")

cld_2022

top_yields_2022 <- cld_2022 %>%
  group_by(Treatment) %>%
  filter(emmean == max(emmean)) %>%
  ungroup()

top_yields_2022
```


### Graph_2022

```{r}
N_response_curve_2022 <- 
ggplot(yield_2022_dataframe, aes(x=Nrate, y=Yield_Mgha, color=Treatment))+
  geom_point(data=yield_2022_dataframe %>% filter(Treatment == "FR"), 
             aes(x=Nrate, y=Yield_Mgha, color="FR"), size=2.5, shape ="triangle") +  
  geom_point(data=yield_2022_dataframe %>% filter(Treatment == "CR"), 
             aes(x=Nrate, y=Yield_Mgha, color="CR"), size=2.5, shape ="triangle") +  
  #geom_point(data=yield_2022_dataframe, size=2.5, shape ="triangle")+ #this is the mean values
  geom_point(data=yield_2022, size=1, alpha=0.4, shape ="triangle")+ #this are the raw values
  scale_color_manual(values=c("#0072B2","#FFCC66"), name = "Treatment", labels = c('Continuous Rice (CR)','Fallow Rice (FR)'))+
  scale_x_continuous(name=expression("N rate (kg N ha"^{-1}*")"), limits = c(-20, 320), breaks = seq(0, 300, by=50), expand =c(0,0))+
  #scale_x_continuous(name=expression("N rate (kg N ha"^{-1}*")"), limits = c(-20, 280), breaks = c(0, 115, 155, 185, 225, 260), expand =c(0,0))+ #limits = c(0, 
  scale_y_continuous(name= expression("Yield (Mg ha"^{-1}*")"), limits = c(0, 22), breaks = seq(0, 22, by = 2.5), expand =c(0,0))+
  #geom_errorbar(data=yield_2022_dataframe, aes(ymin=Yield_Mgha-Yield_Mgha_se, ymax=Yield_Mgha+Yield_Mgha_se), width=8, size=0.7)+
  theme_classic()+
  geom_smooth(data = yield_2022, method = "lm", formula = y ~ poly(x, 2), se = FALSE)+
  #geom_vline(xintercept = c(0, 115, 155, 185, 225, 260), linetype = "twodash", color = "black") +
  theme(axis.text = element_text(size = 14), axis.title = element_text(size=16))+
  theme(legend.text = element_text(size = 12),legend.title = element_text(size = 14))+
  theme(plot.title = element_text(hjust = 0.5, size = 20, face = "bold"))+
  theme(legend.position = "bottom")+
  ggtitle(expression("Yield: 2022"))+
  annotate(
  "text",
  x = c(0),
  y = yield_2022_dataframe %>% 
       filter(Treatment == "FR", Nrate == 0) %>% 
        mutate(Yield_Mgha_plus_higher = Yield_Mgha + 1) %>% 
        pull(Yield_Mgha_plus_higher),
  label = "*",
  size = 7,
  vjust = 0
  )+
# Vertical line for CR
geom_segment(
  aes(x = optimal_results %>% filter(Treatment == "CR", Year == "2022") %>% pull(Nrate_optimal), 
      xend = optimal_results %>% filter(Treatment == "CR", Year == "2022") %>% pull(Nrate_optimal), 
      y = 0,  # Start exactly from 0 on y-axis
      yend = optimal_results %>% filter(Treatment == "CR", Year == "2022") %>% pull(Yield_max)),
  linetype = "twodash", color = "#0072B2", size = 0.6
) +
# Vertical line for FR
geom_segment(
  aes(x = optimal_results %>% filter(Treatment == "FR", Year == "2022") %>% pull(Nrate_optimal), 
      xend = optimal_results %>% filter(Treatment == "FR", Year == "2022") %>% pull(Nrate_optimal), 
      y = 0,  # Start exactly from 0 on y-axis
      yend = optimal_results %>% filter(Treatment == "FR", Year == "2022") %>% pull(Yield_max)),
  linetype = "twodash", color = "#FFCC66", size = 0.6
) +

# Horizontal line for CR
geom_segment(
  aes(y = optimal_results %>% filter(Treatment == "CR", Year == "2022") %>% pull(Yield_max), 
      yend = optimal_results %>% filter(Treatment == "CR", Year == "2022") %>% pull(Yield_max), 
      x = -20,  # Start exactly from 0 on x-axis
      xend = optimal_results %>% filter(Treatment == "CR", Year == "2022") %>% pull(Nrate_optimal)),
  linetype = "twodash", color = "#0072B2", size = 0.6
) +
# Horizontal line for FR
geom_segment(
  aes(y = optimal_results %>% filter(Treatment == "FR", Year == "2022") %>% pull(Yield_max), 
      yend = optimal_results %>% filter(Treatment == "FR", Year == "2022") %>% pull(Yield_max), 
      x = -20,  # Start exactly from 0 on x-axis
      xend = optimal_results %>% filter(Treatment == "FR", Year == "2022") %>% pull(Nrate_optimal)),
  linetype = "twodash", color = "#FFCC66", size = 0.6
)+
  stat_regline_equation(data=yield_2022,
                      aes(x=Nrate, y=Yield_Mgha, color=Treatment, group = Treatment, 
                          label = paste(..rr.label..)),
                      formula = y ~ poly(x, 2, raw = TRUE),
                      show.legend = FALSE, label.x = 0, label.y = c(16.5, 19))+
   stat_regline_equation(data=yield_2022,
                      aes(x=Nrate, y=Yield_Mgha, color=Treatment, group = Treatment, 
                          label = paste(..eq.label..)),
                      formula = y ~ poly(x, 2, raw = TRUE),
                      show.legend = FALSE, label.x = 0, label.y = c(17.5, 20))+
    geom_curve(x = top_yields_2022 %>% 
                 filter(Treatment == "FR") %>% 
                 mutate(NrateF = as.numeric(paste(NrateF))) %>% 
                 pull(NrateF), 
                 y = top_yields_2022 %>% 
                 filter(Treatment == "FR") %>% 
                 pull(emmean),
               xend = top_yields_2022 %>% 
                 filter(Treatment == "CR") %>% 
                 mutate(NrateF = as.numeric(paste(NrateF))) %>% 
                 pull(NrateF), 
               yend = top_yields_2022 %>% 
                 filter(Treatment == "CR") %>% 
                 pull(emmean),
               color = 1, size=1,
               curvature = -0.2)+
  annotate(
  "text",
  x =   (top_yields_2022 %>% 
                 filter(Treatment == "FR") %>% 
                 mutate(NrateF = as.numeric(paste(NrateF))) %>% 
                 pull(NrateF)+
       top_yields_2022 %>% 
                 filter(Treatment == "CR") %>% 
                 mutate(NrateF = as.numeric(paste(NrateF))) %>% 
                 pull(NrateF))/2,
  y = mean(top_yields_2022 %>% 
                 filter(Treatment == "FR") %>% 
                 pull(emmean),
           top_yields_2022 %>% 
                 filter(Treatment == "CR") %>% 
                 pull(emmean)),
  label = "ns",
  size = 5,
  vjust = -2,
  hjust = 0.1 )
  

N_response_curve_2022
```

## 2023 

### Statical test, comparisons by N rate and Treatment

```{r}
model_2023 <- lmer(Yield_Mgha ~ NrateF*Treatment+(1|Blk:Treatment)+(1|Blk), data=yield_2023)

anova(model_2023)

field_means_2023 = emmeans(model_2023,spec = 'Treatment',by = 'NrateF')
field_effects_2023 = contrast(field_means_2023, method = 'pairwise', adjust = "Tukey")

summary(field_effects_2023) 
cld(field_means_2023)

emmeans(model_2023, ~ Treatment + NrateF)
cld_2023 <- cld(emmeans(model_2023, ~ Treatment + NrateF),adjust = "Sidak")

cld_2023

top_yields_2023 <- cld_2023 %>%
  group_by(Treatment) %>%
  filter(emmean == max(emmean)) %>%
  ungroup()
```


### Graph_2023

```{r}
N_response_curve_2023 <- 
ggplot(yield_2023_dataframe, aes(x=Nrate, y=Yield_Mgha, color=Treatment))+
  geom_point(data=yield_2023_dataframe, size=2.5, shape ="square")+ #this is the mean values
  geom_point(data=yield_2023, size=1, alpha=0.4, shape ="square")+ #this are the raw values
  scale_color_manual(values=c("#0072B2","#FFCC66"), name = "Treatment", labels = c('Continuous Rice (CR)','Fallow Rice (FR)'))+
  scale_x_continuous(name=expression("N rate (kg N ha"^{-1}*")"), limits = c(-20, 320), breaks = seq(0, 300, by=50), expand =c(0,0))+
  #scale_x_continuous(name=expression("N rate (kg N ha"^{-1}*")"), limits = c(-20, 280), breaks = c(0, 90, 120, 150, 180, 210), expand =c(0,0))+ #limits = c(0, 
  scale_y_continuous(name= expression("Yield (Mg ha"^{-1}*")"), limits = c(0, 22), breaks = seq(0, 22, by = 2.5), expand =c(0,0))+
  #geom_errorbar(data=yield_2023_dataframe, aes(ymin=Yield_Mgha-Yield_Mgha_se, ymax=Yield_Mgha+Yield_Mgha_se), width=8, size=0.7)+
  theme_classic()+
  geom_smooth(data = yield_2023, method = "lm", formula = y ~ poly(x, 2), se = FALSE)+
  #geom_vline(xintercept = c(0, 115, 155, 185, 225, 260), linetype = "twodash", color = "black") +
  theme(axis.text = element_text(size = 14), axis.title = element_text(size=16))+
  theme(legend.text = element_text(size = 12),legend.title = element_text(size = 14))+
  theme(plot.title = element_text(hjust = 0.5, size = 20, face = "bold"))+
  ggtitle(expression("Yield: 2023"))+
annotate(
  "text",
  x = c(0),
  y = yield_2023_dataframe %>% 
       filter(Treatment == "FR", Nrate == 0) %>% 
        mutate(Yield_Mgha_plus_higher = Yield_Mgha + 1) %>% 
        pull(Yield_Mgha_plus_higher),
  label = "*",
  size = 7,
  vjust = 0
  )+
# Vertical line for CR
geom_segment(
  aes(x = optimal_results %>% filter(Treatment == "CR", Year == "2023") %>% pull(Nrate_optimal), 
      xend = optimal_results %>% filter(Treatment == "CR", Year == "2023") %>% pull(Nrate_optimal), 
      y = 0,  # Start exactly from 0 on y-axis
      yend = optimal_results %>% filter(Treatment == "CR", Year == "2023") %>% pull(Yield_max)),
  linetype = "twodash", color = "#0072B2", size = 0.6
) +
# Vertical line for FR
geom_segment(
  aes(x = optimal_results %>% filter(Treatment == "FR", Year == "2023") %>% pull(Nrate_optimal), 
      xend = optimal_results %>% filter(Treatment == "FR", Year == "2023") %>% pull(Nrate_optimal), 
      y = 0,  # Start exactly from 0 on y-axis
      yend = optimal_results %>% filter(Treatment == "FR", Year == "2023") %>% pull(Yield_max)),
  linetype = "twodash", color = "#FFCC66", size = 0.6
) +

# Horizontal line for CR
geom_segment(
  aes(y = optimal_results %>% filter(Treatment == "CR", Year == "2023") %>% pull(Yield_max), 
      yend = optimal_results %>% filter(Treatment == "CR", Year == "2023") %>% pull(Yield_max), 
      x = -20,  # Start exactly from 0 on x-axis
      xend = optimal_results %>% filter(Treatment == "CR", Year == "2023") %>% pull(Nrate_optimal)),
  linetype = "twodash", color = "#0072B2", size = 0.6
) +
# Horizontal line for FR
geom_segment(
  aes(y = optimal_results %>% filter(Treatment == "FR", Year == "2023") %>% pull(Yield_max), 
      yend = optimal_results %>% filter(Treatment == "FR", Year == "2023") %>% pull(Yield_max), 
      x = -20,  # Start exactly from 0 on x-axis
      xend = optimal_results %>% filter(Treatment == "FR", Year == "2023") %>% pull(Nrate_optimal)),
  linetype = "twodash", color = "#FFCC66", size = 0.6
)+
    geom_curve(x = top_yields_2023 %>% 
                 filter(Treatment == "FR") %>% 
                 mutate(NrateF = as.numeric(paste(NrateF))) %>% 
                 pull(NrateF), 
                 y = top_yields_2023 %>% 
                 filter(Treatment == "FR") %>% 
                 pull(emmean)+0.1,
               xend = top_yields_2023 %>% 
                 filter(Treatment == "CR") %>% 
                 mutate(NrateF = as.numeric(paste(NrateF))) %>% 
                 pull(NrateF), 
               yend = top_yields_2023 %>% 
                 filter(Treatment == "CR") %>% 
                 pull(emmean)+0.1,
               color = 1, size=1,
               curvature = -0.2)+
  stat_regline_equation(data=yield_2023,
                      aes(x=Nrate, y=Yield_Mgha, color=Treatment, group = Treatment, 
                          label = paste(..rr.label..)),
                      formula = y ~ poly(x, 2, raw = TRUE),
                      show.legend = FALSE, label.x = 0, label.y = c(16.5, 19))+
   stat_regline_equation(data=yield_2023,
                      aes(x=Nrate, y=Yield_Mgha, color=Treatment, group = Treatment, 
                          label = paste(..eq.label..)),
                      formula = y ~ poly(x, 2, raw = TRUE),
                      show.legend = FALSE, label.x = 0, label.y = c(17.5, 20))+
  annotate(
  "text",
  x =   (top_yields_2023 %>% 
                 filter(Treatment == "FR") %>% 
                 mutate(NrateF = as.numeric(paste(NrateF))) %>% 
                 pull(NrateF)+
       top_yields_2023 %>% 
                 filter(Treatment == "CR") %>% 
                 mutate(NrateF = as.numeric(paste(NrateF))) %>% 
                 pull(NrateF))/2,
  y = mean(top_yields_2023 %>% 
                 filter(Treatment == "FR") %>% 
                 pull(emmean),
           top_yields_2023 %>% 
                 filter(Treatment == "CR") %>% 
                 pull(emmean)),
  label = "ns",
  size = 5,
  vjust = -1.3,
  hjust = 0.6)
  

N_response_curve_2023

```

## Average 

### Statical test, comparisons by N rate and Treatment

```{r}
model_average <- lmer(Yield_Mgha ~ NrateF*Treatment+(1|Blk:Treatment)+(1|Blk), data=yield_average)

anova(model_average)

field_means_average = emmeans(model_average,spec = 'Treatment',by = 'NrateF')
field_effects_average = contrast(field_means_average, method = 'pairwise', adjust = "Tukey")

summary(field_effects_average) 
cld(field_means_average)

emmeans(model_average, ~ Treatment + NrateF)
cld_average <- cld(emmeans(model_average, ~ Treatment + NrateF),adjust = "Sidak")

top_yields_average <- cld_average %>%
  group_by(Treatment) %>%
  filter(emmean == max(emmean)) %>%
  ungroup()
```


### Graph_average_with_equations

```{r}
N_response_curve_average_v1 <- 
ggplot(yield_average_dataframe, aes(x=Nrate, y=Yield_Mgha, color=Treatment))+
  geom_point(data=yield_average_dataframe, size=2.5)+ #this is the mean values
  geom_point(data=yield_average, size=1, alpha=0.4, aes(shape=Year))+ #this are the raw values
  scale_color_manual(values=c("#0072B2","#FFCC66"), name = "Treatment", labels = c('Continuous Rice (CR)','Fallow Rice (FR)'))+
  scale_x_continuous(name=expression("N Rate (kg N ha"^{-1}*")"), limits = c(-5, 290), breaks = c(0, 115, 155, 185, 225, 260))+ #limits = c(0, 
  scale_y_continuous(name= expression("Yield (Mg ha"^{-1}*")"), limits = c(0, 20), breaks = seq(0, 20, by = 2.5))+ #, limits = c(0, 16000), expand = c(0, 0), breaks =
  #geom_errorbar(data=yield_average_dataframe, aes(ymin=Yield_Mgha-Yield_Mgha_se, ymax=Yield_Mgha+Yield_Mgha_se), width=8, size=0.7)+
  theme_classic()+
  theme(axis.text = element_text(size = 10), axis.title = element_text(size=10))+
  geom_smooth(data = yield_average, method = "lm", formula = y ~ poly(x, 2), se = FALSE)+
  #geom_vline(xintercept = c(0, 115, 155, 185, 225, 260), linetype = "twodash", color = "black") +
  theme(legend.text = element_text(size = 10),legend.title = element_text(size = 14))+
  stat_regline_equation(data=yield_average,
                      aes(x=Nrate, y=Yield_Mgha, color=Treatment, group = Treatment, 
                          label = paste(..rr.label..)),
                      formula = y ~ poly(x, 2, raw = TRUE),
                      show.legend = FALSE, label.x = 0, label.y = c(16.5, 19))+
   stat_regline_equation(data=yield_average,
                      aes(x=Nrate, y=Yield_Mgha, color=Treatment, group = Treatment, 
                          label = paste(..eq.label..)),
                      formula = y ~ poly(x, 2, raw = TRUE),
                      show.legend = FALSE, label.x = 0, label.y = c(17.5, 20))+
  
  theme(plot.title = element_text(hjust = 0.5, size = 15))+
  ggtitle(expression("average"))+
  annotate(
  "text",
  x = c(0),
  y = yield_average_dataframe %>% 
        filter(Treatment == "FR", Nrate == 0) %>% 
        mutate(Yield_Mgha_plus_higher = Yield_Mgha + 1) %>% 
        pull(Yield_Mgha_plus_higher),
  label = "*",
  size = 7,
  vjust = 0
  )+
  geom_vline(
    aes(xintercept = optimal_results %>% filter(Treatment == "CR") %>% filter(Year == "average") %>% pull(Nrate_optimal)),
    linetype = "twodash", color = "#0072B2", size = 1
  )+ 
  geom_vline(
    aes(xintercept = optimal_results %>% filter(Treatment == "FR") %>% filter(Year == "average") %>% pull(Nrate_optimal)),
    linetype = "twodash", color = "#FFCC66", size = 1
  )+
    geom_curve(x = top_yields_average %>% 
                 filter(Treatment == "FR") %>% 
                 mutate(NrateF = as.numeric(paste(NrateF))) %>% 
                 pull(NrateF), 
                 y = top_yields_average %>% 
                 filter(Treatment == "FR") %>% 
                 pull(emmean)+0.2,
               xend = top_yields_average %>% 
                 filter(Treatment == "CR") %>% 
                 mutate(NrateF = as.numeric(paste(NrateF))) %>% 
                 pull(NrateF), 
               yend = top_yields_average %>% 
                 filter(Treatment == "CR") %>% 
                 pull(emmean)+0.2,
               color = 1, size=1,
               curvature = -0.2,
               linetype = "twodash")+
  annotate(
  "text",
  x =   (top_yields_average %>% 
                 filter(Treatment == "FR") %>% 
                 mutate(NrateF = as.numeric(paste(NrateF))) %>% 
                 pull(NrateF)+
       top_yields_average %>% 
                 filter(Treatment == "CR") %>% 
                 mutate(NrateF = as.numeric(paste(NrateF))) %>% 
                 pull(NrateF))/2,
  y = mean(top_yields_average %>% 
                 filter(Treatment == "FR") %>% 
                 pull(emmean),
           top_yields_average %>% 
                 filter(Treatment == "CR") %>% 
                 pull(emmean)),
  label = "ns",
  size = 5,
  vjust = -0.9,
  hjust = 0.6)
  

N_response_curve_average_v1
```

### Graph_average 

```{r}
N_response_curve_average <- 
ggplot(yield_average, aes(x=Nrate, y=Yield_Mgha, color=Treatment, shape=Year))+
  geom_point(data=yield_average, size=2)+ #this is the mean values+
    geom_segment(x = -10, 
            y = yield_average_dataframe %>% 
                 filter(Nrate==0)  %>%
                 filter(Treatment == "FR") %>% 
                 pull(Yield_Mgha),
            xend = 10, 
            yend = yield_average_dataframe %>% 
                 filter(Nrate==0)  %>%
                 filter(Treatment == "FR") %>% 
                 pull(Yield_Mgha),
               color = "#FFCC66", size=2)+
  geom_segment(x = -10, 
            y = yield_average_dataframe %>% 
                 filter(Nrate==0)  %>%
                 filter(Treatment == "CR") %>% 
                 pull(Yield_Mgha),
            xend = 10, 
            yend = yield_average_dataframe %>% 
                 filter(Nrate==0)  %>%
                 filter(Treatment == "CR") %>% 
                 pull(Yield_Mgha),
               color = "#0072B2", size=2)+
  #geom_point(data=yield_average, size=1, alpha=0.4)+ #this are the raw values
  scale_color_manual(values=c("#0072B2","#FFCC66"), name = "Treatment", labels = c('Continuous Rice (CR)','Fallow Rice (FR)'))+
 scale_x_continuous(name=expression("N Rate (kg N ha"^{-1}*")"), limits = c(-20, 280), breaks = c(0, 115, 155, 185, 225, 260), expand =c(0,0))+ #limits = c(0, 
  scale_y_continuous(name= expression("Yield (Mg ha"^{-1}*")"), limits = c(0, 22), breaks = seq(0, 22, by = 2.5), expand =c(0,0))+
  theme_classic()+
  #geom_smooth(data = yield_average, aes(group = Treatment), method = "lm", formula = y ~ poly(x, 2), se = FALSE)+
  #geom_vline(xintercept = c(0, 115, 155, 185, 225, 260), linetype = "twodash", color = "black") +
  #stat_regline_equation(data=yield_average,
   #                   aes(x=Nrate, y=Yield_Mgha, color=Treatment, group = Treatment, 
    #                      label = paste(..rr.label..)),
     #                 formula = y ~ poly(x, 2, raw = TRUE),
      #                show.legend = FALSE, label.x = 0, label.y = c(16.5, 19))+
   #stat_regline_equation(data=yield_average,
    #                  aes(x=Nrate, y=Yield_Mgha, color=Treatment, group = Treatment, 
     #                     label = paste(..eq.label..)),
      #                formula = y ~ poly(x, 2, raw = TRUE),
       #               show.legend = FALSE, label.x = 0, label.y = c(17.5, 20))+
  theme(axis.text = element_text(size = 14), axis.title = element_text(size=16))+
  theme(legend.text = element_text(size = 12),legend.title = element_text(size = 14))+
  theme(plot.title = element_text(hjust = 0.5, size = 20, face = "bold"))+
  ggtitle(expression("Yield: All"))+
  annotate(
  "text",
  x = c(0),
  y = yield_average_dataframe %>% 
        filter(Treatment == "FR", Nrate == 0) %>% 
        mutate(Yield_Mgha_plus_higher = Yield_Mgha + 2) %>% 
        pull(Yield_Mgha_plus_higher),
  label = "*",
  size = 7,
  vjust = 0
  )+
  theme(legend.position = "bottom")
  


N_response_curve_average

```

# Combine all plots

```{r}
Yields <- ggarrange(N_response_curve_2021,
                    N_response_curve_2022,
                    N_response_curve_2023,
                    #N_response_curve_average,
                               nrow = 1,
                               ncol = 3,
                               common.legend = TRUE,
                               #legend.grob = get_legend(N_response_curve_average),
                               legend= "bottom")

Yields

ggsave(filename = "Yields_no_avg.jpg",  # Include the file extension here
       plot = Yields,              # Specify the plot
       path = "C:/Users/zhang/Documents/GitHub/FallowRice_ContinuousRice_AgronomicPerformance/Figures",
       dpi = 400,
       height = 20, width = 50, units = "cm")

ggsave(filename = "2022_NResponse.jpg",  # Include the file extension here
       plot = N_response_curve_2022,              # Specify the plot
       path = "C:/Users/zhang/Documents/GitHub/FallowRice_ContinuousRice_AgronomicPerformance/Figures",
       dpi = 400,
       height = 15, width = 15, units = "cm")
```

# Combine 0N yields into 1 excel file 

```{r}
all_means <- rbind(as.data.frame(field_means_2021) %>% mutate(Year = 2021),
                   as.data.frame(field_means_2022) %>% mutate(Year = 2022),
                   as.data.frame(field_means_2023) %>% mutate(Year = 2023),
                   as.data.frame(field_means_average) %>% mutate(Year = "Avg")
                  ) %>% arrange(Year) %>% filter(NrateF == "0") %>%
  mutate(yield = round(emmean, 1))

write_xlsx(all_means, "C:/Users/zhang/Documents/GitHub/FallowRice_ContinuousRice_AgronomicPerformance/Yield/Yield_by_year_0N.xlsx")
```


# Zero N

```{r}
zero_N <- yield_average %>% filter(Nrate == 0)

model_zero <- lmer(Yield_Mgha ~ Treatment*Year+(1|Blk), data=zero_N)

zero_means_average = emmeans(model_zero,spec = 'Treatment', by = "Year")
zero_effects_average = contrast(zero_means_average, method = 'pairwise', adjust = "Tukey")
summary(zero_effects_average)
```

# Graphical abstract

```{r}
N_response_curve_graphical_abstract <- 
ggplot(yield_2022_dataframe, aes(x=Nrate, y=Yield_Mgha, color=Treatment))+
  geom_point(data=yield_2022_dataframe %>% filter(Treatment == "FR"), 
             aes(x=Nrate, y=Yield_Mgha, color="FR"), size=2.5) +  
  geom_point(data=yield_2022_dataframe %>% filter(Treatment == "CR"), 
             aes(x=Nrate, y=Yield_Mgha, color="CR"), size=2.5) +  
  #geom_point(data=yield_2022_dataframe, size=2.5, shape ="triangle")+ #this is the mean values
  #geom_point(data=yield_2022, size=1, alpha=0.4, shape ="triangle")+ #this are the raw values
  scale_color_manual(values=c("#0072B2","#FFCC66"), name = "Treatment", labels = c('Continuous Rice (CR)','Fallow Rice (FR)'))+
  scale_x_continuous(name=expression("N rate (kg N ha"^{-1}*")"), limits = c(-20, 280), breaks = seq(0, 300, by=50), expand =c(0,0))+ #limits = c(0, 
  scale_y_continuous(name= expression("Yield (Mg ha"^{-1}*")"), limits = c(0, 22), breaks = seq(0, 22, by = 2.5), expand =c(0,0))+
  #geom_errorbar(data=yield_2022_dataframe, aes(ymin=Yield_Mgha-Yield_Mgha_se, ymax=Yield_Mgha+Yield_Mgha_se), width=8, size=0.7)+
  theme_classic()+
  geom_smooth(data = yield_2022, method = "lm", formula = y ~ poly(x, 2), se = FALSE)+
  #geom_vline(xintercept = c(0, 115, 155, 185, 225, 260), linetype = "twodash", color = "black") +
  theme(axis.text = element_text(size = 14), axis.title = element_text(size=16))+
  theme(legend.text = element_text(size = 12),legend.title = element_text(size = 14))+
  theme(plot.title = element_text(hjust = 0.5, size = 20, face = "bold"))+
  theme(legend.position = "bottom")+
  #ggtitle(expression("Yield: 2022"))+
  annotate(
  "text",
  x = c(0),
  y = yield_2022_dataframe %>% 
       filter(Treatment == "FR", Nrate == 0) %>% 
        mutate(Yield_Mgha_plus_higher = Yield_Mgha + 1) %>% 
        pull(Yield_Mgha_plus_higher),
  label = "*",
  size = 7,
  vjust = 0
  )+
geom_segment(
  aes(x = optimal_results %>% filter(Treatment == "CR", Year == "2022") %>% pull(Nrate_optimal), 
      xend = optimal_results %>% filter(Treatment == "CR", Year == "2022") %>% pull(Nrate_optimal), 
      y = 0,  # Start exactly from 0 on y-axis
      yend = optimal_results %>% filter(Treatment == "CR", Year == "2022") %>% pull(Yield_max)),
  linetype = "twodash", color = "#0072B2", size = 0.6
) +
# Vertical line for FR
geom_segment(
  aes(x = optimal_results %>% filter(Treatment == "FR", Year == "2022") %>% pull(Nrate_optimal), 
      xend = optimal_results %>% filter(Treatment == "FR", Year == "2022") %>% pull(Nrate_optimal), 
      y = 0,  # Start exactly from 0 on y-axis
      yend = optimal_results %>% filter(Treatment == "FR", Year == "2022") %>% pull(Yield_max)),
  linetype = "twodash", color = "#FFCC66", size = 0.6
) +

# Horizontal line for CR
geom_segment(
  aes(y = optimal_results %>% filter(Treatment == "CR", Year == "2022") %>% pull(Yield_max), 
      yend = optimal_results %>% filter(Treatment == "CR", Year == "2022") %>% pull(Yield_max), 
      x = -20,  # Start exactly from 0 on x-axis
      xend = optimal_results %>% filter(Treatment == "CR", Year == "2022") %>% pull(Nrate_optimal)),
  linetype = "twodash", color = "#0072B2", size = 0.6
) +
# Horizontal line for FR
geom_segment(
  aes(y = optimal_results %>% filter(Treatment == "FR", Year == "2022") %>% pull(Yield_max), 
      yend = optimal_results %>% filter(Treatment == "FR", Year == "2022") %>% pull(Yield_max), 
      x = -20,  # Start exactly from 0 on x-axis
      xend = optimal_results %>% filter(Treatment == "FR", Year == "2022") %>% pull(Nrate_optimal)),
  linetype = "twodash", color = "#FFCC66", size = 0.6
)+
    geom_curve(x = top_yields_2022 %>% 
                 filter(Treatment == "FR") %>% 
                 mutate(NrateF = as.numeric(paste(NrateF))) %>% 
                 pull(NrateF), 
                 y = top_yields_2022 %>% 
                 filter(Treatment == "FR") %>% 
                 pull(emmean),
               xend = top_yields_2022 %>% 
                 filter(Treatment == "CR") %>% 
                 mutate(NrateF = as.numeric(paste(NrateF))) %>% 
                 pull(NrateF), 
               yend = top_yields_2022 %>% 
                 filter(Treatment == "CR") %>% 
                 pull(emmean),
               color = 1, size=1,
               curvature = -0.2)+
  annotate(
  "text",
  x =   (top_yields_2022 %>% 
                 filter(Treatment == "FR") %>% 
                 mutate(NrateF = as.numeric(paste(NrateF))) %>% 
                 pull(NrateF)+
       top_yields_2022 %>% 
                 filter(Treatment == "CR") %>% 
                 mutate(NrateF = as.numeric(paste(NrateF))) %>% 
                 pull(NrateF))/2,
  y = mean(top_yields_2022 %>% 
                 filter(Treatment == "FR") %>% 
                 pull(emmean),
           top_yields_2022 %>% 
                 filter(Treatment == "CR") %>% 
                 pull(emmean)),
  label = "ns",
  size = 5,
  vjust = -2,
  hjust = 0.1 )+
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()
        )+
theme(legend.title=element_blank())
  

N_response_curve_graphical_abstract

ggsave(filename = "N_response_curve_graphical_abstract.jpg",  # Include the file extension here
       plot = N_response_curve_graphical_abstract,              # Specify the plot
       path = "C:/Users/zhang/Documents/GitHub/FallowRice_ContinuousRice_AgronomicPerformance/Figures",
       dpi = 800,
       height = 10, width = 10.5, units = "cm")
```