---
title: "Apparent Fertilizer Nitrogen  Recovery Efficiency (FNRE)"
author: "Zhang Zhenglin"
output:
  pdf_document:
    toc: yes
  html_notebook:
    toc: yes
    toc_float: yes
editor_options:
  markdown:
    wrap: sentence
---

# Necessary libraries

```{r echo=FALSE,message=FALSE,warning=FALSE}
library(ggplot2)
theme_set(theme_bw())
library(emmeans)
library(multcomp)
library(PLS205)
library(lme4)
library(lmerTest)
library(multcompView)
library(car)
library(Rmisc) 
library(dplyr) #https://r4ds.had.co.nz/ (Chapter 3, Chapter 5, look at filter and select)
library(stringr) 
library(readxl)
library(writexl)
library(ggpubr)
```

# Read and check data

```{r}
#read data
master = read_excel('C:/Users/zhang/Documents/GitHub/FallowRice_ContinuousRice_AgronomicPerformance/N uptake/N uptake calculations from SIF data/N_uptake_Maturity_Summed_Clean.xlsx', sheet = 1)

#making sure that the master datFNREame will be correct 
master <- master %>% filter(Stage=="Maturity") %>% filter(Topdress != 1)
```


# Calculate FNRE for each plot

```{r}

# Define the FNRE calculation function
calculate_FNRE <- function(data) {
  
  # Ensure the datFNREame is grouped by Year, Block, and Treatment
  FNRE_df <- data %>%
    group_by(Year, Blk, Treatment) %>%
    
    # Nest the data within each Year, Blk, Treatment group
    do({
      # Separate 0N plot (reference plot with no nitrogen application)
      zero_nitrogen_plot <- .[.$Nrate_kgha == 0,]
      
      # Ensure there's a 0N plot to reference
      if (nrow(zero_nitrogen_plot) == 0) {
        stop("No 0N plot found in one of the groups!")
      }
      
      # Calculate FNRE for the rest of the plots in the group
      mutate(., FNRE = (N_total_kgha - zero_nitrogen_plot$N_total_kgha) / Nrate_kgha)
    })
  
  # Ungroup to return a regular datFNREame
  FNRE_df <- FNRE_df %>%
    ungroup()
  
  return(FNRE_df)
}


master_with_FNRE <- calculate_FNRE(master) %>% 
  mutate(FNRE = FNRE*100) %>% 
  filter(Nrate_kgha !=0) %>% 
  mutate(NrateF = as.factor(Nrate_kgha))

#write_xlsx(master_with_FNRE, "C:/Users/zhang/Desktop/master_with_FNRE.xlsx")
#manuallychecked and all looks correct
```

# Split data by year

```{r}
FNRE_all <- master_with_FNRE %>% 
  #filter(Year != 2023) %>% 
  filter(Topdress!=1) %>% 
  filter(Stage=="Maturity") %>%
  mutate(Year= as.factor(Year))

FNRE_2021 <- master_with_FNRE %>% 
  filter(Year == 2021) %>% 
  filter(Topdress!=1) %>% 
  filter(Stage=="Maturity") %>%
  mutate(Year= as.factor(Year))

FNRE_2022 <- master_with_FNRE %>% 
  filter(Year == 2022) %>% 
  filter(Topdress!=1) %>% 
  filter(Stage=="Maturity") %>%
  mutate(Year= as.factor(Year))

FNRE_2023 <- master_with_FNRE %>% 
  filter(Year == 2023) %>% 
  filter(Topdress!=1) %>% 
  filter(Stage=="Maturity") %>%
  mutate(Year= as.factor(Year))

table(FNRE_2021$Nrate_kgha)
```

# General linear model to do some exploratory analysis

Seems that there is an effect of Nrate and Year. But no treatment effects. 

```{r}
all_factors_model <- lm(FNRE ~ Nrate_kgha*Treatment*Year, data = FNRE_all)

pls205_diagnostics(all_factors_model)

anova(all_factors_model)
```

# 2021

## Statistical tests

```{r}
model_2021 <- lmer(FNRE ~ NrateF*Treatment+(1|Blk:Treatment)+(1|Blk), data=FNRE_2021)

pls205_diagnostics(model_2021, EU="Blk:Treatment")

anova(model_2021)

means_2021 = emmeans(model_2021,spec = 'Treatment',by = 'NrateF')
effects_2021 = contrast(means_2021, method = 'pairwise', adjust = "Tukey")

summary(effects_2021) 
cld(means_2021)

emmeans(model_2021, ~ Treatment + NrateF)
cld(emmeans(model_2021, ~ Treatment + NrateF),adjust = "Sidak")
cld_2021 <- cld(emmeans(model_2021, ~ Treatment + NrateF),adjust = "Sidak") %>% mutate(Nrate_kgha = as.numeric(paste(NrateF))) %>% mutate(group =.group)
```


## 2021 graph

### Graphing dataframe

```{r}
graphing_2021 <- FNRE_2021 %>% 
    group_by(Treatment, Nrate_kgha) %>% 
   mutate(FNRE_se = sd(FNRE)/sqrt(3)) %>% 
  summarise(FNRE = mean(FNRE),
            FNRE_se = mean(FNRE_se)) %>%
  left_join(cld_2021 %>% select(Treatment, Nrate_kgha, group), by = c("Treatment", "Nrate_kgha"))
```

### ggplot_2021


```{r}
FNRE_2021_graph <- 
ggplot(graphing_2021, aes(x=Nrate_kgha, y=FNRE, color=Treatment))+
  geom_point(data=graphing_2021, size=2.5)+ #this is the mean values
  geom_point(data=FNRE_2021, size=1, alpha=0.4)+ #this are the raw values
  scale_color_manual(values=c("#0072B2","#FFCC66"), name = "Treatment", labels = c('Continuous Rice (CR)','Fallow Rice (FR)'))+
  scale_x_continuous(name=expression("N Rate (kg N ha"^{-1}*")"), limits = c(80, 280), breaks = c(115, 155, 185, 225, 260))+
  scale_y_continuous(name= expression("FNRE (%)"), limits = c(0, 100), breaks = seq(0, 100, by = 20))+ 
  theme_classic()+
  geom_smooth(data = FNRE_2021, method = "lm", se = FALSE)+

  theme(axis.text = element_text(size = 14), axis.title = element_text(size=16))+
  theme(legend.text = element_text(size = 12),legend.title = element_text(size = 14))+
  theme(plot.title = element_text(hjust = 0.5, size = 20, face = "bold"))+
  ggtitle(expression("FNRE: 2021"))

FNRE_2021_graph
```


# 2022

## Statistical tests

```{r}
model_2022 <- lmer(FNRE ~ NrateF*Treatment+(1|Blk:Treatment)+(1|Blk), data=FNRE_2022)

pls205_diagnostics(model_2022, EU="Blk:Treatment")

anova(model_2022)

means_2022 = emmeans(model_2022,spec = 'Treatment',by = 'NrateF')
effects_2022 = contrast(means_2022, method = 'pairwise', adjust = "Tukey")

summary(effects_2022) 
cld(means_2022)

emmeans(model_2022, ~ Treatment + NrateF)
cld(emmeans(model_2022, ~ Treatment + NrateF),adjust = "Sidak")
cld_2022 <- cld(emmeans(model_2022, ~ Treatment + NrateF),adjust = "Sidak") %>% mutate(Nrate_kgha = as.numeric(paste(NrateF))) %>% mutate(group =.group)
```


## 2022 graph

### Graphing dataframe

```{r}
graphing_2022 <- FNRE_2022 %>% 
    group_by(Treatment, Nrate_kgha) %>% 
   mutate(FNRE_se = sd(FNRE)/sqrt(3)) %>% 
  summarise(FNRE = mean(FNRE),
            FNRE_se = mean(FNRE_se)) %>%
  left_join(cld_2022 %>% select(Treatment, Nrate_kgha, group), by = c("Treatment", "Nrate_kgha"))
```

### ggplot_2022
```{r}
FNRE_2022_graph <- 
ggplot(graphing_2022, aes(x=Nrate_kgha, y=FNRE, color=Treatment))+
  geom_point(data=graphing_2022, size=2.5,shape ="triangle")+ #this is the mean values
  geom_point(data=FNRE_2022, size=1, alpha=0.4,shape ="triangle")+ #this are the raw values
  scale_color_manual(values=c("#0072B2","#FFCC66"), name = "Treatment", labels = c('Continuous Rice (CR)','Fallow Rice (FR)'))+
  scale_x_continuous(name=expression("N Rate (kg N ha"^{-1}*")"), limits = c(80, 280), breaks = c(115, 155, 185, 225, 260))+
  scale_y_continuous(name= expression("FNRE (%)"), limits = c(0, 100), breaks = seq(0, 100, by = 20))+ 
  theme_classic()+
  geom_smooth(data = FNRE_2022, method = "lm", se = FALSE)+

  theme(axis.text = element_text(size = 14), axis.title = element_text(size=16))+
  theme(legend.text = element_text(size = 12),legend.title = element_text(size = 14))+
  theme(plot.title = element_text(hjust = 0.5, size = 20, face = "bold"))+
  ggtitle(expression("FNRE: 2022"))

FNRE_2022_graph
```


# 2023

## Statistical tests

```{r}
model_2023 <- lmer(FNRE ~ NrateF*Treatment+(1|Blk:Treatment)+(1|Blk), data=FNRE_2023)

pls205_diagnostics(model_2023, EU="Blk:Treatment")

anova(model_2023)

means_2023 = emmeans(model_2023,spec = 'Treatment',by = 'NrateF')
effects_2023 = contrast(means_2023, method = 'pairwise', adjust = "Tukey")

summary(effects_2023) 
cld(means_2023)

emmeans(model_2023, ~ Treatment + NrateF)
cld(emmeans(model_2023, ~ Treatment + NrateF),adjust = "Sidak")
cld_2023 <- cld(emmeans(model_2023, ~ Treatment + NrateF),adjust = "Sidak") %>% mutate(Nrate_kgha = as.numeric(paste(NrateF))) %>% mutate(group =.group)
```

## 2023 graph

### Graphing dataframe

```{r}
graphing_2023 <- FNRE_2023 %>% 
    group_by(Treatment, Nrate_kgha) %>% 
   mutate(FNRE_se = sd(FNRE)/sqrt(3)) %>% 
  summarise(FNRE = mean(FNRE),
            FNRE_se = mean(FNRE_se)) %>%
  left_join(cld_2023 %>% select(Treatment, Nrate_kgha, group), by = c("Treatment", "Nrate_kgha"))
```

### ggplot_2023

```{r}
FNRE_2023_graph <- 
ggplot(graphing_2023, aes(x=Nrate_kgha, y=FNRE, color=Treatment))+
  geom_point(data=graphing_2023, size=2.5, shape ="square")+ #this is the mean values
  geom_point(data=FNRE_2023, size=1, alpha=0.4, shape ="square")+ #this are the raw values
  scale_color_manual(values=c("#0072B2","#FFCC66"), name = "Treatment", labels = c('Continuous Rice (CR)','Fallow Rice (FR)'))+
  scale_x_continuous(name=expression("N Rate (kg N ha"^{-1}*")"), limits = c(80, 280), breaks = c(90,120,150,180,210))+
  scale_y_continuous(name= expression("FNRE (%)"), limits = c(0, 100), breaks = seq(0, 100, by = 20))+ 
  theme_classic()+
  geom_smooth(data = FNRE_2023, method = "lm", se = FALSE)+

  theme(axis.text = element_text(size = 14), axis.title = element_text(size=16))+
  theme(legend.text = element_text(size = 12),legend.title = element_text(size = 14))+
  theme(plot.title = element_text(hjust = 0.5, size = 20, face = "bold"))+
  ggtitle(expression("FNRE: 2023"))

FNRE_2023_graph
```

# All together

## Statistical tests

```{r}
model_average <- lmer(FNRE ~ NrateF*Treatment+(1|Blk:Treatment)+(1|Blk), data=FNRE_all)

anova(model_average)

field_means_average = emmeans(model_average,spec = 'Treatment',by = 'NrateF')
field_effects_average = contrast(field_means_average, method = 'pairwise', adjust = "Tukey")

summary(field_effects_average) 
cld(field_means_average)

emmeans(model_average, ~ Treatment + NrateF)
cld(emmeans(model_average, ~ Treatment + NrateF),adjust = "Sidak")
cld_average <- cld(emmeans(model_average, ~ Treatment + NrateF),adjust = "Sidak")
```


## All together graph

```{r}
FNRE_all_graph <- 
ggplot(FNRE_all, aes(x=Nrate_kgha, y=FNRE, color=Treatment, shape = Year))+
  geom_point(size=2.5)+ #this is the mean values
  #geom_point(data=FNRE_2023, size=1, alpha=0.4, shape ="square")+ #this are the raw values
  scale_color_manual(values=c("#0072B2","#FFCC66"), name = "Treatment", labels = c('Continuous Rice (CR)','Fallow Rice (FR)'))+
  scale_x_continuous(name=expression("N Rate (kg N ha"^{-1}*")"), limits = c(80, 280), breaks = seq(80, 280, by = 50))+
  scale_y_continuous(name= expression("FNRE (%)"), limits = c(0, 100), breaks = seq(0, 100, by = 20))+ 
  theme_classic()+
  geom_smooth(aes(group = Treatment), method = "lm", se = FALSE)+
  theme(axis.text = element_text(size = 14), axis.title = element_text(size=16))+
  theme(legend.text = element_text(size = 12),legend.title = element_text(size = 14))+
  theme(plot.title = element_text(hjust = 0.5, size = 20, face = "bold"))+
  ggtitle(expression("FNRE: All"))+
  theme(legend.position = "bottom")

FNRE_all_graph
```


# Combine into 1 graph

```{r}
FNRE_combined <- ggarrange(FNRE_2021_graph,
                               FNRE_2022_graph,
                               FNRE_2023_graph,
                               #FNRE_all_graph,
                               nrow = 1,
                               #ncol = 2,
                               #common.legend = TRUE,
                               legend.grob = get_legend(FNRE_all_graph),
                               legend= "bottom")


ggsave(filename = "FNRE_combined_all_year.jpg",  # Include the file extension here
       plot = FNRE_combined,              # Specify the plot
       path = "C:/Users/zhang/Documents/GitHub/FallowRice_ContinuousRice_AgronomicPerformance/Figures",
       dpi = 400,
       height = 15, width = 40, units = "cm")
```

# Combine into 1 excel file 

```{r}
all_means <- rbind(as.data.frame(means_2021) %>% mutate(Year = 2021),
                   as.data.frame(means_2022) %>% mutate(Year = 2022),
                   as.data.frame(means_2023) %>% mutate(Year = 2023)
) %>% arrange(Treatment,Year)

write_xlsx(all_means, "D:/Academics/UC Davis/School Work/Linquist Lab/Data/R stats/Agronomic paper/N uptake/FNRE/FNRE_by_year_Nrate.xlsx")

```

